---
title: "Home"
author: "Jing Huang"
date: "`r Sys.Date()`"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
output:
  html_document:
    toc: true
    toc_depth: 2  # Up to two depths of headings
    theme: united  # Many options for theme
---

<style>
/* Adjust general text line spacing */
p {line-height: 1.75; font-size: 18px;}
h1 {font-size: 24px; text-align: center;} 
h2 {font-size: 22px; } 
/* Adjust line spacing in numbered or bulleted lists */
ul, ol {line-height: 1.5;}
</style>


Welcome to my website! I am a Ph.D. candidate in Educational Psychology and Research Methodology at Purdue University, under the guidance of Professor Hua-hua Chang. If you’d like to get in touch, please click on “**About**” or “**LinkedIn**” at the top right corner.

## Education
<hr style="border: none; border-top: 3px solid black; width: 100%; margin-top: 1px; margin-bottom: 5px;" />


```{r, warning=FALSE,echo=FALSE, message=FALSE}
# Load necessary libraries
library(tibble)
library(knitr)  # Optional, for kable to display tables
library(kableExtra)

# Create a tribble
data <- tribble(
  ~Year, ~Degree, ~Institution,
  "Aug.2023 - <br>Present", "PhD", "Purdue University<br>Educational Psychology and Research Methodology",
  "Sep.2020 – <br>Jun.2023","M.A.", "East China Normal University<br>Educational Psychology",
  "Sep.2016 – <br>Jun.2020", "B.S.","East China Normal University<br>Statistics"
)

# Display the table with adjustable column widths, no full width, and text size adjustments
kable(data, "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, 
                position = "left", 
                font_size = 18) %>%   # Adjust the overall font size of the table
  row_spec(0, bold = TRUE, font_size = 20) %>%  # Adjust font size and boldness for the header
  column_spec(1, width = "20%") %>%  # Adjust column width for Year
  column_spec(2, width = "15%") %>%  # Adjust column width for Degree
  column_spec(3, width = "65%")      # Adjust column width for Institution_and_Major
```

## Awards, Honors, & Fellowships
<hr style="border: none; border-top: 3px solid black; width: 100%; margin-top: 1px; margin-bottom: 5px;" />

```{r, warning=FALSE,echo=FALSE, message=FALSE}
# Load necessary libraries
library(tibble)
library(knitr)  # Optional, for kable to display tables
library(kableExtra)

# Create a tribble
data <- tribble(
  ~Year, ~Content,
  "Mar. 2023", "Ross Fellowship",
  "Oct. 2022", "National Scholarship",
  "Oct. 2022", "Outstanding Student",
  "Oct. 2021", "Shu Qing Encouragement Scholarship",
  "Dec. 2020", "The Third Prize in the Contemporary Graduate Statistical Contest in Modeling",
  "Jul. 2020", "The Second Prize in the COVID-19 Data Analysis Contest",
  "Nov. 2019", "The Third Prize for the Contemporary Undergraduate Statistical Contest in Modeling",
  "Nov. 2019", "Shanghai Popular Science Education Innovation Award",
  "Feb. 2019", "The Meritorious Winner in the Interdisciplinary Contest in Modeling (ICM)",
)

# Display the table with adjustable column widths, no full width, and text size adjustments
kable(data, "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, 
                position = "left", 
                font_size = 18) %>%   # Adjust the overall font size of the table
  row_spec(0, bold = TRUE, font_size = 20) %>%  # Adjust font size and boldness for the header
  column_spec(1, width = "30%") %>%  # Adjust column width for Year
  column_spec(2, width = "70%")   # Adjust column width for Degree
```

	


